---
title: "MATH 216 Homework 5"
author: "Andrew Holtz"
output: html_document
---


## Admistrative:

Please indicate

* Who you collaborated with: No one :( 
* Roughly how much time you spent on this HW: 3-4 hours
* What gave you the most trouble: Figuring out of to translate rmd to shiny 
* Any comments you have: I wanted to add more features to the shiny app, such
as total number of words, but I could not figure out how to get the app to
refresh. 

```{r, echo = FALSE}

library(dplyr)
library(stringr)
library(shiny)

# Note the solutions to all exercises are at the end of the file.

# Introducing the tm = "text mining" package:  it has various tools for advanced
# text processing (beyond simple string manipulation).  The outputs of tm
# functions are used in other packages, including the wordcloud package.

# Install the following new packages:
library(tm)
library(wordcloud)
library(SnowballC)
library(wordcloud)
library(memoise)
```




## Question 1:

* Pick three books from [Project Gutenberg](https://www.gutenberg.org/) and make
a "single-file" Shiny app based on file `App.R`
    + showing the corresponding wordcloud for a given book
    + that has "toggle" functionality to switch between the three books
* Note: Project Gutenberg tends to have older books whose copyright has expired.
* Install all necessary packages on your Middlebury Shiny server account
following the instructions given in Lec16 Shiny.
* Upload your app to the Middlebury Shiny server and replace the NHL link with
the link for your app [here](https://aholtz.shinyapps.io/Homework_5/), so that 
when you Knit the document a working hyperlink shows.

Hints:

* Get your code completely working for a non-Shiny app first, then build your
app slowly.
* If you get stuck, please ask for help sooner rather than later. I don't want 
people spinning their wheels on this HW this late in the semester.
* Consider using `if` and `else` statements to switch out which text to show the
wordcloud for. Note this isn't the only way to do this. Ex:

```{r, echo = FALSE}


meta <-
  readLines("Data/metamorphosis.txt", encoding="UTF-8") %>%
  as.character()

beowulf <- 
  readLines("Data/beowulf.txt", encoding="UTF-8") %>%
  as.character()
  
faust <- 
  readLines("Data/faust.txt", encoding="UTF-8") %>%
  as.character() %>% 
  str_replace_all("_Faust._", "") %>% 
  str_replace_all("_Margarete._", "") %>% 
  str_replace_all("__Mephistopheles.__", "") %>% 
  str_replace_all("Mephistophel", "")

meta <- meta %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()

faust <- faust %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("german")) %>%
  stemDocument() %>%
  stripWhitespace()

beowulf <- beowulf %>% 
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()


text <- "Beowulf"

if(text == "Metamorphosis"){
  value <- meta
} else if (text == "Beowulf"){
  value <- beowulf
} else if (text == "Faust"){
  value <- faust
} 

word_cloud <- VectorSource(value) %>% 
  Corpus()
wordcloud(value, scale=c(4,0.5), min.freq = 5, max.words=100, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "Dark2"))









```


